In this experiment main focus is making UDP reliable (RUDP). Reliable UDP is for reliable communication. Our RUDP protocol has been implemented using one of sliding window protocols, Go-Back-N. To make our protocol reliable, we add checksum and sequence number values in the header of packet, use re-transmission and we send back Ack/nAck packets. To control the flow of transmission of data, we use flag values as condition variables. Our protocol is able to transmit large data over networks when the packet size is acceptable. As a future work, congestion control mechanism can be implemented to overcome the processing and memory overheads. Our protocol, security of the transferred data is not considered, providing it can also be done as future work. At the end, in the experiment, source and broker has TCP based connection and rest uses our protocol, we are asked to make UDP part(unreliable part) reliable, we can basically do that via TCP but this is not the problem. We have also examined our protocol versus TCP. TCP hogs all packets that are received until they came to the destination in the expecting order. This might be harmful to performance. One of the problem about TCP is about out-of-order packets. For example, in the multi-player games where only care is about the last position of player not where and what happened about a few milliseconds ago. RUDP modifications, provides most recent packet to achieve that.\\

Note that, all of the network configurations, codings, README file and report have been done by uniformly together. We worked as a pair in design, implementation, report parts and others since, composing, changing or improving any part affected the all other parts. We also use GitHub and Overleaf to make pair programming since they allow working together at the same time for people in a group.
\clearpage